An Open-Source Implementation of the CMPS Algorithm for Assessing Similarity of Bullets

### 2022-03-29 review_responds/review-responds-ju-hofmann2.md

`func_collection.R` is now removed from the supplementary materials since the most helper functions are included in the `cmpsR` package.

> line 70: there is a global assignment for current.max in the function get_CMPS. And it seems a bit confusing for the user who wants to access the code. I suggest that to avoid this global assignment when building a package. I think current.max = max(pos.df$cmps) is equivalent to what is written in the function.

This global assignment is now removed and is replaced by an equivalent for loop.

> It might be good to add a CITATION file and a README.md file to the package.

The `README.md` file and `CITATION` file are now added to the package.

@@

We have added the legend for the lines presented in Figure 4b. And the grey boxes in Figure 4a is now darker than before.

> Figure 9 and Figure 10 on page 14 and page 15: Is there any overlap between KM and KNM? The counts for KM is very small. It might be good to convert the count into probability. (i.e. hist(...,
probability = TRUE))

Thank you for your suggestion. There is no overlap between KM and KNM in Figure 9 and Figure 10. And in order to make the counts more visible, we have converted the counts to XXX

#### Note on the marked article
\

The `marked_article.pdf` in the same folder of the review responds is a marked version of the article, where the new added contents are highlighted in blue. The intention of this file is to allow the reviewers to quickly find out what has been changed for this revision.

### 2022-03-30 review_responds/review-responds-ju-hofmann2.md

---
output:
  pdf_document: default
  html_document: default
---

## Overview

We would like to thank the reviewers for the thorough review and the excellent comments.

@@

> The coding style is not consistent through the article. For instance, in certain places, the objects have "." whereas the other places have "_" (cmps.result.KM, cmps_with_multi_scale). Please make sure that the coding style is kept consistent throughout the article.

Thank you for your advice. The coding style is now consistent both throughout the article and in the `cmpsR` package.

> In supplementary materials, all the functions are placed in a single file named 'func_collection.R'. Please make sure that only similar functions are placed in one file and the file is named such that the name reflects the type of functions within it. This will mean that the file 'func_collection.R' is split into multiple files.

`func_collection.R` is now removed from the supplementary materials. All the helper functions are included in the `cmpsR` package, and the code highlighted in the paper and for reproducing all images is attached separately.

@@

> Hamby44_npeak_result_*.R - Line 17: it seems there is no package called CMPS (it might be cmpsR?)
>
> hamby44_npeak_result_generator.R : The parallelization in ~line 223 in is not working under the window environment, but the following code can make the program works by replacing the mclapply(...) with

We have corrected the package names in `Hamby44_npeak_result_*.R` and modified the parallelization so that it works on both Mac and Windows environments.

#### Note on the **cmpsR** package
\

Note that all the updates of the `cmpsR` package are only available on [github](https://github.com/willju-wangqian/cmpsR). We have not yet submitted the updates to CRAN yet since we are looking forward to your further suggestions and advice and do not want to bother the CRAN teammultiple times. Please make sure that you have the most updated version of the `cmpsR` package (version 0.1.2) from [github](https://github.com/willju-wangqian/cmpsR) before you execute any `R` code that depends on it.

`install_github("willju-wangqian/cmpsR")`

@@

> Page 4, get_segs(x,len=50). Is the len = 50 is the default argument of the function? How does the length of segments is determined? Will the performance of the algorithm change for different
values of len?

We added more details of the parameter `len` in the article. As discussed in the "Algorithm" section after the introduction of the steps, the default values of these parameters are given in the original CMPS paper (Chen et al., 2019) but no cross-validation has been done. The choices of these parameters will affect the final result of the algorithm, and the proposed evaluation framework based on the "Sum of Squares Ratio" could be used to evaluate the parameter choices.

> Page 8, cmps_signature_plot(...). It will be good to add legends within the plot for the black/red
solid line and the red dotted line, and the grey boxes in Figure 4a seem almost invisible.

We have added the legend for the lines presented in Figure 4b and made the grey boxes in Figure 4a darker than before.

@@

> Figure 9 and Figure 10 on page 14 and page 15: Is there any overlap between KM and KNM? The counts for KM is very small. It might be good to convert the count into probability. (i.e. hist(...,
probability = TRUE))

Thank you for your suggestion. There is no overlap between KM and KNM in Figure 9 and Figure 10. And in order to make the counts more visible, we have converted the counts to proportions by group.

### 2022-03-31 review_responds/review-responds-ju-hofmann2.md

> Hamby44_npeak_result_*.R - Line 17: it seems there is no package called CMPS (it might be cmpsR?)
>
> hamby44_npeak_result_generator.R : The parallelization in ~line 223 in is not working under the window environment, but the following code can make the program works by replacing the mclapply(...) with

We have corrected the package names in `Hamby44_npeak_result_*.R` and modified the parallelization so that it works on both Mac and Windows environments.

#### Note on the **cmpsR** package
\

Note that all the updates of the `cmpsR` package are only available on [github](https://github.com/willju-wangqian/cmpsR). We have not yet submitted the updates to CRAN yet since we are looking forward to your further suggestions and advice and do not want to bother the CRAN team multiple times. Please make sure that you have the most updated version of the `cmpsR` package (version 0.1.2) from [github](https://github.com/willju-wangqian/cmpsR) before you execute any `R` code that depends on it.

### 2022-03-31 submissions/resubmission-ju-hofmann2/ju-hofmann.Rmd
ready for re-submission
clean up the folder and finish the revision for this round

---
title: An Open-Source Implementation of the CMPS Algorithm for Assessing Similarity of Bullets
header-includes:
  - \usepackage{amsmath}
  - \usepackage{xcolor}
  - \usepackage{longtable}
  - \usepackage{adjustbox}            
  - \usepackage[font=small,skip=5pt]{caption}
  - \usepackage{subcaption}
  - \usepackage{afterpage}
  - \usepackage{bbm}
author:
  # see ?rjournal_article for more information
  - name: Wangqian W. Ju
    affiliation: Department of Statistics
    address:
    - Center for Statistics and Applications in Forensic Evidence
    - Iowa State University
    - 2438 Osborn Dr
    - Ames, IA 50011
    url: https://github.com/willju-wangqian
    email:  wju@iastate.edu
    orcid: 0000-0002-9977-377X
  - name: Heike Hofmann
    url: https://github.com/heike
    email: hofmann@iastate.edu
    orcid: 0000-0002-9079-593X
    affiliation: Department of Statistics
    address:
    - Center for Statistics and Applications in Forensic Evidence
    - Iowa State University
    - 2438 Osborn Dr
    - Ames, IA 50011
thanks: |
  This work was partially funded by the Center for Statistics and Applications in Forensic Evidence (CSAFE) through Cooperative Agreement 70NANB20H019 between NIST and Iowa State University, which includes activities carried out at Carnegie Mellon University, Duke University, University of California Irvine, University of Virginia, West Virginia University, University of Pennsylvania, Swarthmore College and University of Nebraska, Lincoln.    
abstract: >
  In this paper, we introduce the R package \pkg{cmpsR}, an open-source implementation of the Congruent Matching Profile Segments (CMPS) method developed at the National Institute of Standards and Technology (NIST) for objective comparison of striated tool marks. The functionality of the package is showcased by examples of bullet signatures that come with the package. Graphing tools are implemented in the package as well for users to assess and understand the CMPS results. Initial tests were performed on bullet signatures generated from two sets of 3D scans in the Hamby study under the framework suggested by the R package \pkg{bulletxtrctr}. New metrics based on CMPS scores are introduced and compared with existing metrics. A measure called Sum of squares ratio is included, and how it can be used for evaluating different scans, metrics, or parameters is showcased with the Hamby study data sets. An open-source implementation of the CMPS algorithm makes the algorithm more accessible, generates reproducible results, and facilitates further studies of the algorithm such as methods comparison.
preamble: |
  % Any extra LaTeX you need in the preamble

@@

ADD_LABELS_HIST <- TRUE
```

@@

1.  **cut the comparison signature into consecutive, non-overlapping and equal-length basis segments:** The command \code{get\_segs(x, len=50)} implements this step: it takes bullet signature \code{x} in the format of a numeric vector and cuts it into consecutive, non-overlapping and equal-length segments of length \code{len}, which are referred to as "basis segments". \wj{Note that the parameter} \code{len} \wj{determines the length of a basis segment and thus affects the total number of basis segments, which is the upper limit of the CMPS score of a comparison. The default value of} \code{len} \wj{is 50, which will result in about 25 basis segments for the example data of the package. }

@@

Note that there are several parameters in the CMPS algorithm that \wj{will affect the final results and} are left to the users to decide, such as the length of basis segments \code{seg\_length} in step 1, the number of peaks \code{npeaks\_set} identified on each level in step 2, and the length of the tolerance zone \code{Tx} in both step 2 and 3.
In our implementation of the CMPS algorithm we used the parameters given in the original CMPS paper [@cmps] as the default values for these parameters.
However, the authors state that no cross-validation has been done - there might also be issues with respect to resolution of the scans.
Further research is needed, until then users are advised to think of default values as starting values and consider alternatives. \wj{However, the evaluation framework based on the Sum of Squares Ratio introduced in the later section could be used to evaluate the choices of these parameters. }
The main function that combines all steps in the CMPS algorithm described above is called \code{extract\_feature\_cmps(...)}.
Here we present it with its default parameters.

@@

As presented in the work of @cmps, researchers applied the CMPS method to scans of one of the Hamby sets.
While it is not explicitly stated in the paper, we presume this to be Hamby 252, as only those scans were publicly available at the time. 
In order to show that our implementation of the CMPS algorithm is able to reproduce the results in @cmps and be used for other data sets, we applied our implementation to both Hamby set 252 and Hamby set 44.
For the purpose of reproducibility, we present how we obtained bullet signatures from the Hamby set data and include code in the appendix: for both Hamby 252 and Hamby 44, we started with scans in the form of x3p files in the database.
Following the framework proposed by @aoas, we used the same set of parameters, removed damaged bullet scans, obtained bullet signatures for each bullet land engraving, and removed outliers in bullet signatures.
Note that researchers of @cmps applied the CMPS algorithm to bullet signatures as well but used a framework different from ours.
However, since their work is not open-source, we were not able to follow their framework and were only able to reproduce the results for Hamby set 252 qualitatively.

@@

```{r result1_252, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 252; outliers are removed in bullet signatures; \\texttt{seg\\_length = 50}, \\texttt{Tx = 25}, \\texttt{npeaks\\_set = c(5,3,1)} ", fig.height=3}
# [4] "span1=0.25, span2=0.03, rm_outliers = TRUE, 5025, 531"
# knitr::include_graphics("img/hamby252_v1.png", dpi = 100)
# CMPS_hamby252_results$plot[[2]]

p1 <- metric_plot_helper(
  CMPS_hamby252_results_seg$cmps.table[[2]], "cmps.max",
  subtitle = "npeaks_set: 5-3-1, seg_length: 50") +
  xlab(labels[1])
p2 <- metric_plot_helper(
  CMPS_hamby252_results_seg$cmps.table[[2]], "cmps.maxbar",
  subtitle = "npeaks_set: 5-3-1, seg_length: 50") +
  xlab(labels[4])

@@

```{r result1_44, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 44; outliers are removed in bullet signatures; \\texttt{seg\\_length = 61}, \\texttt{Tx = 30}, \\texttt{npeaks\\_set = c(5,3,1)} ", fig.height=3, warning=FALSE}
p1 <- metric_plot_helper(
  CMPS_hamby44_results_seg$cmps.table[[3]], "cmps.max",
  subtitle = "npeaks_set: 5-3-1, seg_length: 61") +
  xlab(labels[1])
p2 <- metric_plot_helper(
  CMPS_hamby44_results_seg$cmps.table[[3]], "cmps.maxbar",
  subtitle = "npeaks_set: 5-3-1, seg_length: 61") +
  xlab(labels[4])

>>>>

---
title: An Open-Source Implementation of the CMPS Algorithm for Assessing Similarity of Bullets
header-includes:
  - \usepackage{amsmath}
  - \usepackage{xcolor}
  - \usepackage{longtable}
  - \usepackage{adjustbox}            
  - \usepackage[font=small,skip=5pt]{caption}
  - \usepackage{subcaption}
  - \usepackage{afterpage}
  - \usepackage{bbm}
author:
  # see ?rjournal_article for more information
  - name: Wangqian Ju
    affiliation: Department of Statistics
    address:
    - Center for Statistics and Applications in Forensic Evidence
    - Iowa State University
    - 2438 Osborn Dr
    - Ames, IA 50011
    url: https://github.com/willju-wangqian
    email:  wju@iastate.edu
    orcid: 0000-0002-9977-377X
  - name: Heike Hofmann
    url: https://github.com/heike
    email: hofmann@iastate.edu
    orcid: 0000-0002-9079-593X
    affiliation: Department of Statistics
    address:
    - Center for Statistics and Applications in Forensic Evidence
    - Iowa State University
    - 2438 Osborn Dr
    - Ames, IA 50011
thanks: |
  This work was partially funded by the Center for Statistics and Applications in Forensic Evidence (CSAFE) through Cooperative Agreement 70NANB20H019 between NIST and Iowa State University, which includes activities carried out at Carnegie Mellon University, Duke University, University of California Irvine, University of Virginia, West Virginia University, University of Pennsylvania, Swarthmore College and University of Nebraska, Lincoln.    
abstract: >
  In this paper, we introduce the R package \pkg{cmpsR}, an open-source implementation of the Congruent Matching Profile Segments (CMPS) method developed at the National Institute of Standards and Technology (NIST) for objective comparison of striated tool marks. The functionality of the package is showcased by examples of bullet signatures that come with the package. Graphing tools are implemented in the package as well for users to assess and understand the CMPS results. Initial tests were performed on bullet signatures generated from two sets of 3D scans in the Hamby study under the framework suggested by the R package \pkg{bulletxtrctr}. New metrics based on CMPS scores are introduced and compared with existing metrics. A measure called Sum of squares ratio is included, and how it can be used for evaluating different scans, metrics, or parameters is showcased with the Hamby study data sets. An open-source implementation of the CMPS algorithm makes the algorithm more accessible, generates reproducible results, and facilitates further studies of the algorithm such as methods comparison.
preamble: |
  % Any extra LaTeX you need in the preamble

@@

ADD_LABELS_HIST <- FALSE
```

@@

1.  **cut the comparison signature into consecutive, non-overlapping and equal-length basis segments:** The command \code{get\_segs(x, len=50)} implements this step: it takes bullet signature \code{x} in the format of a numeric vector and cuts it into consecutive, non-overlapping and equal-length segments of length \code{len}, which are referred to as "basis segments". Note that the parameter \code{len} determines the length of a basis segment and thus affects the total number of basis segments, which is the upper limit of the CMPS score of a comparison. The default value of \code{len} is 50, which will result in about 25 basis segments for the example data of the package.

@@

Note that there are several parameters in the CMPS algorithm that will affect the final results and are left to the users to decide, such as the length of basis segments \code{seg\_length} in step 1, the number of peaks \code{npeaks\_set} identified on each level in step 2, and the length of the tolerance zone \code{Tx} in both step 2 and 3.
In our implementation of the CMPS algorithm we used the parameters given in the original CMPS paper [@cmps] as the default values for these parameters.
However, the authors state that no cross-validation has been done - there might also be issues with respect to resolution of the scans.
Further research is needed, until then users are advised to think of default values as starting values and consider alternatives. However, the evaluation framework based on the Sum of Squares Ratio introduced in the later section could be used to evaluate the choices of these parameters. 
The main function that combines all steps in the CMPS algorithm described above is called \code{extract\_feature\_cmps(...)}.
Here we present it with its default parameters.

@@

As presented in the work of @cmps, researchers applied the CMPS method to scans of one of the Hamby sets.
While it is not explicitly stated in the paper, we presume this to be Hamby 252, as only those scans were publicly available at the time. 
In order to show that our implementation of the CMPS algorithm is able to reproduce the results in @cmps and be used for other data sets, we applied our implementation to both Hamby set 252 and Hamby set 44.
Here we present how we obtained bullet signatures from the Hamby set data: for both Hamby 252 and Hamby 44, we started with scans in the form of x3p files in the database.
Following the framework proposed by @aoas, we used the same set of parameters, removed damaged bullet scans, obtained bullet signatures for each bullet land engraving, and removed outliers in bullet signatures.
Note that researchers of @cmps applied the CMPS algorithm to bullet signatures as well but used a framework different from ours.
However, since their work is not open-source, we were not able to follow their framework and were only able to reproduce the results for Hamby set 252 qualitatively.

@@

```{r result1_252, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 252; outliers are removed in bullet signatures; \\texttt{seg\\_length = 50}, \\texttt{Tx = 25}, \\texttt{npeaks\\_set = c(5,3,1)}; instead of showing the counts on the y-axis, we present the observed proportions conditioned on KM group and KNM group to enhance the visibility of the bars ", fig.height=3}
# [4] "span1=0.25, span2=0.03, rm_outliers = TRUE, 5025, 531"
# knitr::include_graphics("img/hamby252_v1.png", dpi = 100)
# CMPS_hamby252_results$plot[[2]]

p1 <- metric_plot_helper(
  CMPS_hamby252_results_seg$cmps.table[[2]], "cmps.max",
  subtitle = "npeaks_set: 5-3-1, seg_length: 50") +
  xlab(labels[1]) + 
  theme(axis.text.x = element_text(size=7))
p2 <- metric_plot_helper(
  CMPS_hamby252_results_seg$cmps.table[[2]], "cmps.maxbar",
  subtitle = "npeaks_set: 5-3-1, seg_length: 50") +
  xlab(labels[4])

@@

```{r result1_44, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 44; outliers are removed in bullet signatures; \\texttt{seg\\_length = 61}, \\texttt{Tx = 30}, \\texttt{npeaks\\_set = c(5,3,1)}; instead of showing the counts on the y-axis, we present the observed proportions conditioned on KM group and KNM group to enhance the visibility of the bars ", fig.height=3, warning=FALSE}
p1 <- metric_plot_helper(
  CMPS_hamby44_results_seg$cmps.table[[3]], "cmps.max",
  subtitle = "npeaks_set: 5-3-1, seg_length: 61") +
  xlab(labels[1]) + 
  theme(axis.text.x = element_text(size=7))
p2 <- metric_plot_helper(
  CMPS_hamby44_results_seg$cmps.table[[3]], "cmps.maxbar",
  subtitle = "npeaks_set: 5-3-1, seg_length: 61") +
  xlab(labels[4])

### 2022-03-31 submissions/resubmission-ju-hofmann2/ju-hofmann.tex
update variable names in ju-hofmann.R
clean up the folder and finish the revision for this round

% !TeX root = RJwrapper.tex
\title{An Open-Source Implementation of the CMPS Algorithm for Assessing
Similarity of Bullets}
\author{by Wangqian W. Ju and Heike Hofmann}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{cut the comparison signature into consecutive, non-overlapping
  and equal-length basis segments:} The command
  \code{get\_segs(x, len=50)} implements this step: it takes bullet
  signature \code{x} in the format of a numeric vector and cuts it into
  consecutive, non-overlapping and equal-length segments of length
  \code{len}, which are referred to as ``basis segments''.
  \wj{Note that the parameter} \code{len}
  \wj{determines the length of a basis segment and thus affects the total number of basis segments, which is the upper limit of the CMPS score of a comparison. The default value of}
  \code{len}
  \wj{is 50, which will result in about 25 basis segments for the example data of the package. }
\item
  \textbf{identify candidate positions:} For each basis segment a set of
  candidate registration positions on the comparison signature is
  identified based on the segment's similarity to the reference
  signature. In a first step, the cross-correlation function of the
  segment to the reference is calculated, then a number of positions
  with high correlation values are identified as candidate positions. In
  case multiple segment lengths are considered, the length of each basis
  segment is expanded (by default it is doubled) and these two steps are
  repeated. Only when candidate positions coincide (or are similar
  enough), they are considered further. \autoref{fig:segplots} and
  \autoref{fig:seg_all} illustrate these ideas.

@@

Note that there are several parameters in the CMPS algorithm that
\wj{will affect the final results and} are left to the users to decide,
such as the length of basis segments \code{seg\_length} in step 1, the
number of peaks \code{npeaks\_set} identified on each level in step 2,
and the length of the tolerance zone \code{Tx} in both step 2 and 3. In
our implementation of the CMPS algorithm we used the parameters given in
the original CMPS paper \citep{cmps} as the default values for these
parameters. However, the authors state that no cross-validation has been
done - there might also be issues with respect to resolution of the
scans. Further research is needed, until then users are advised to think
of default values as starting values and consider alternatives.
\wj{However, the evaluation framework based on the Sum of Squares Ratio introduced in the later section could be used to evaluate the choices of these parameters. }
The main function that combines all steps in the CMPS algorithm
described above is called \code{extract\_feature\_cmps(...)}. Here we
present it with its default parameters.

@@

As presented in the work of \citet{cmps}, researchers applied the CMPS
method to scans of one of the Hamby sets. While it is not explicitly
stated in the paper, we presume this to be Hamby 252, as only those
scans were publicly available at the time. In order to show that our
implementation of the CMPS algorithm is able to reproduce the results in
\citet{cmps} and be used for other data sets, we applied our
implementation to both Hamby set 252 and Hamby set 44. For the purpose
of reproducibility, we present how we obtained bullet signatures from
the Hamby set data and include code in the appendix: for both Hamby 252
and Hamby 44, we started with scans in the form of x3p files in the
database. Following the framework proposed by \citet{aoas}, we used the
same set of parameters, removed damaged bullet scans, obtained bullet
signatures for each bullet land engraving, and removed outliers in
bullet signatures. Note that researchers of \citet{cmps} applied the
CMPS algorithm to bullet signatures as well but used a framework
different from ours. However, since their work is not open-source, we
were not able to follow their framework and were only able to reproduce
the results for Hamby set 252 qualitatively.

@@

\caption{Distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ for Hamby 252; outliers are removed in bullet signatures; \texttt{seg\_length = 50}, \texttt{Tx = 25}, \texttt{npeaks\_set = c(5,3,1)} }\label{fig:result1_252}
\end{figure}
\end{Schunk}

@@

\caption{Distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ for Hamby 44; outliers are removed in bullet signatures; \texttt{seg\_length = 61}, \texttt{Tx = 30}, \texttt{npeaks\_set = c(5,3,1)} }\label{fig:result1_44}
\end{figure}
\end{Schunk}

@@

\begin{itemize}
\tightlist
\item
  \texttt{hamby*\_result\_generator.R}: these R scripts take the
  processed data of Hamby set 252 and Hamby set 44, generate preliminary
  results used in the paper, and save the results in the \texttt{.csv}
  format in the folder \texttt{data-csv}.
\item
  \texttt{rds\_generator.R}: this R script takes the generated
  \texttt{.csv} files and produce \texttt{CMPSpaper\_results.rds}.
  \texttt{CMPSpaper\_results.rds} is identical to
  \texttt{data/CMPSpaper\_results.rds} and is used generate figures and
  other results presented in the paper.
\item
  \texttt{func\_collection.R}: this R script contains some helper
  functions used by other R scripts.
\end{itemize}

@@

\address{%
Wangqian W. Ju\\
Department of Statistics\\%
Center for Statistics and Applications in Forensic Evidence\\ Iowa State
University\\ 2438 Osborn Dr\\ Ames, IA 50011\\
%
\url{https://github.com/willju-wangqian}\\%
\textit{ORCiD: \href{https://orcid.org/0000-0002-9977-377X}{0000-0002-9977-377X}}\\%
\href{mailto:wju@iastate.edu}{\nolinkurl{wju@iastate.edu}}%
}

>>>>

% !TeX root = RJwrapper.tex
\title{An Open-Source Implementation of the CMPS Algorithm for Assessing
Similarity of Bullets}
\author{by Wangqian Ju and Heike Hofmann}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{cut the comparison signature into consecutive, non-overlapping
  and equal-length basis segments:} The command
  \code{get\_segs(x, len=50)} implements this step: it takes bullet
  signature \code{x} in the format of a numeric vector and cuts it into
  consecutive, non-overlapping and equal-length segments of length
  \code{len}, which are referred to as ``basis segments''. Note that the
  parameter \code{len} determines the length of a basis segment and thus
  affects the total number of basis segments, which is the upper limit
  of the CMPS score of a comparison. The default value of \code{len} is
  50, which will result in about 25 basis segments for the example data
  of the package.
\item
  \textbf{identify candidate positions:} For each basis segment a set of
  candidate registration positions on the comparison signature is
  identified based on the segment's similarity to the reference
  signature. In a first step, the cross-correlation function of the
  segment to the reference is calculated, then a number of positions
  with high correlation values are identified as candidate positions. In
  case multiple segment lengths are considered, the length of each basis
  segment is expanded (by default it is doubled) and these two steps are
  repeated. Only when candidate positions coincide (or are similar
  enough), they are considered further. \autoref{fig:segplots} and
  \autoref{fig:seg_all} illustrate these ideas.

@@

Note that there are several parameters in the CMPS algorithm that will
affect the final results and are left to the users to decide, such as
the length of basis segments \code{seg\_length} in step 1, the number of
peaks \code{npeaks\_set} identified on each level in step 2, and the
length of the tolerance zone \code{Tx} in both step 2 and 3. In our
implementation of the CMPS algorithm we used the parameters given in the
original CMPS paper \citep{cmps} as the default values for these
parameters. However, the authors state that no cross-validation has been
done - there might also be issues with respect to resolution of the
scans. Further research is needed, until then users are advised to think
of default values as starting values and consider alternatives. However,
the evaluation framework based on the Sum of Squares Ratio introduced in
the later section could be used to evaluate the choices of these
parameters. The main function that combines all steps in the CMPS
algorithm described above is called \code{extract\_feature\_cmps(...)}.
Here we present it with its default parameters.

@@

As presented in the work of \citet{cmps}, researchers applied the CMPS
method to scans of one of the Hamby sets. While it is not explicitly
stated in the paper, we presume this to be Hamby 252, as only those
scans were publicly available at the time. In order to show that our
implementation of the CMPS algorithm is able to reproduce the results in
\citet{cmps} and be used for other data sets, we applied our
implementation to both Hamby set 252 and Hamby set 44. Here we present
how we obtained bullet signatures from the Hamby set data: for both
Hamby 252 and Hamby 44, we started with scans in the form of x3p files
in the database. Following the framework proposed by \citet{aoas}, we
used the same set of parameters, removed damaged bullet scans, obtained
bullet signatures for each bullet land engraving, and removed outliers
in bullet signatures. Note that researchers of \citet{cmps} applied the
CMPS algorithm to bullet signatures as well but used a framework
different from ours. However, since their work is not open-source, we
were not able to follow their framework and were only able to reproduce
the results for Hamby set 252 qualitatively.

@@

\caption{Distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ for Hamby 252; outliers are removed in bullet signatures; \texttt{seg\_length = 50}, \texttt{Tx = 25}, \texttt{npeaks\_set = c(5,3,1)}; instead of showing the counts on the y-axis, we present the observed proportions conditioned on KM group and KNM group to enhance the visibility of the bars }\label{fig:result1_252}
\end{figure}
\end{Schunk}

@@

\caption{Distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ for Hamby 44; outliers are removed in bullet signatures; \texttt{seg\_length = 61}, \texttt{Tx = 30}, \texttt{npeaks\_set = c(5,3,1)}; instead of showing the counts on the y-axis, we present the observed proportions conditioned on KM group and KNM group to enhance the visibility of the bars }\label{fig:result1_44}
\end{figure}
\end{Schunk}

@@

\begin{itemize}
\tightlist
\item
  \texttt{hamby*\_result\_generator.R}: these R scripts take the
  processed data of Hamby set 252 and Hamby set 44, generate preliminary
  results used in the paper, and save the results in the \texttt{.csv}
  format in the folder \texttt{data-csv}. Please make sure that the
  package versions of \texttt{bulletxtrctr} and \texttt{cmpsR} meet the
  requirements.
\item
  \texttt{rds\_generator.R}: this R script takes the generated
  \texttt{.csv} files and produce \texttt{CMPSpaper\_results.rds}.
  \texttt{CMPSpaper\_results.rds} is identical to
  \texttt{data/CMPSpaper\_results.rds} and is used generate figures and
  other results presented in the paper.
\end{itemize}

@@

\address{%
Wangqian Ju\\
Department of Statistics\\%
Center for Statistics and Applications in Forensic Evidence\\ Iowa State
University\\ 2438 Osborn Dr\\ Ames, IA 50011\\
%
\url{https://github.com/willju-wangqian}\\%
\textit{ORCiD: \href{https://orcid.org/0000-0002-9977-377X}{0000-0002-9977-377X}}\\%
\href{mailto:wju@iastate.edu}{\nolinkurl{wju@iastate.edu}}%
}
